---
title: "**PerformanceAnalytics** Plotting Using Additional Plotting Engines"
subtitle: "features added in GSoC 2019"
author: "Zeheng 'Zenith' Zhou, Justin M. Shea, and Brian G. Peterson"
output: html_document
always_allow_html: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Multiple Plotting Engine

The main purpose of this update is to add multiple plotting engines into the current plotting functions. Functions modified for now are:
- chart.Boxplot
- chart.TimeSeries
- chart.CumReturns
- chart.Drawdown
- charts.PerformanceSummary

The engines added onto the functions are:
- ggplot2 (plot.engine = "ggplot2")
- dygraphPlot (plot.engine  = "dygraph")
- googleVis (plot.engine = "googlevis")
- plotly (plotly)

A demo of different plot engines in different functions will be shown as below:

```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
library(PerformanceAnalytics)
library(xts)
library(zoo)
library(ggplot2)
library(plotly)
library(dygraphs)
library(googleVis)
library(gridExtra)

data("edhec")
```

# chart.Boxplot

This function includes plotting engine: "ggplot2","plotly".

## plotly

```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.Boxplot(edhec, plot.engine = "plotly", main="demo")
```

## ggplot2
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.Boxplot(edhec, plot.engine = "ggplot2", main="demo")
```



# chart.TimeSeries

This function includes plotting engine: "ggplot2","plotly","googlevis","dygraph"

## dygraphPlot
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.TimeSeries(edhec,plot.engine = "dygraph",main="demo")
```

## plotly
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.TimeSeries(edhec,plot.engine = "plotly",main="demo")
```

## ggplot2
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.TimeSeries(edhec,plot.engine = "ggplot2",main="demo")
```


# chart.CumReturns

This function includes plotting engine: `plotly`,`googlevis`,`dygraph`, and `ggplot2`


## dygraphPlot
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.CumReturns(edhec,plot.engine = "dygraph",main="demo")
```

## plotly
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.CumReturns(edhec,plot.engine = "plotly",main="demo")
```

## ggplot2
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.CumReturns(edhec,plot.engine = "ggplot2",main="demo")
```



# chart.Drawdown

This function includes plotting engine: "ggplot2","plotly","googlevis","dygraph"

## dygraphPlot
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.Drawdown(edhec,plot.engine = "dygraph",main="demo")
```

## plotly
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.Drawdown(edhec,plot.engine = "plotly",main="demo")
```

## ggplot2
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
chart.Drawdown(edhec,plot.engine = "ggplot2",main="demo")
```


# charts.PerformanceSummary

This function includes plotting engine: "ggplot2","plotly"

## plotly
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
charts.PerformanceSummary(edhec,plot.engine = "plotly",main="demo")
```

## ggplot2
```{r echo = TRUE, warning = FALSE, message = FALSE, error=FALSE}
charts.PerformanceSummary(edhec,plot.engine = "ggplot2",main="demo")
```

